### 2014-03-12 src/methodology.Rnw
update
udpate

Finally, to ensure accuracy of our observations, each criteria described has been run four times, and the results are averaged to produce the final result.

One of our research questions was to compare the utility of operator
selection --- especially statement deletion --- with random sampling of mutants,
Since we use PIT, which is a bytecode oriented mutation engine, implementing statement deletion
directly is very hard. However, we can approximate statement deletion by combining different
bytecode operators, as explained later.

@@

We used several different sampling criterias.

@@

\subsubsection{Statement Deletion:}
The basic statement deletion was modeled on the work by Deng et
al.~\cite{deng2013empirical}. The operations on single statements was modeled
using \pitvmc, \pitnvmc, \pitcc, \pitemv, \pitri
for simple statements, and using \pitrc for control structures,
which replaced the boolean condition with false, resulting in removal of
the block of statements. The operator for return values was modeled using
\pitrv, which is similar.  The operators for \textit{while,for},
and \textit{if} statements were modeled using \pitdc,
which replaced the boolean condition with true, which removed the effect
of conditional. The \textit{switch} statement deletion was modeled using
\pitrs which replaced the first 100 labels with default label,
resulting in the switch element getting deleted. (Due to the constraints
of the architecture of PIT only the first 100 labels were replaced). The
\textit{try catch} was not necessary at bytecode level.  Finally, to get an
accurate estimation of the effect of true statement deletion, we grouped
the mutants by line, and considered a single virtual mutant (That is, the
total number of mutants is equal to the total number of lines). Further,
killing any mutant from a line resulted in marking the virtual mutant
for that line as killed. This gave us the mutation score for the virtual
statement deletion operator.  We note that the approximation of simple
statement deletion, especially when arithmetic operators are involved is not
complete. However, as seen in Figure~\ref{fig:op}, the number of mutants
produced by \pitm operator is very small. We also note that our
approximation does not account for the increase in ease of detection when
multiple mutations are combined together due to coupling effect. This also
means that not all the lines may be mutated since there may be no applicable
operators. However, given the constraints of a bytecode based mutation system,
we believe that our procedure is reasonable.

>>>>

Finally, to remove random noice, each criteria described has been run four times, and the results are averaged to produce the final result.

One of the criterias we sampled was \textit{statement deletion}.
Since we use PIT, which is a bytecode based mutation engine, implementing direct equivalent of
source code statement deletion is very hard. We were able to approximate statement deletion
by combining different bytecode operators, which is explained in Subsection~\ref{subsec:stmtdel}.

@@

We used several different sampling criterias, based on different strategies of sampling, and what happens when the number of mutants selected falls below a threshold.

@@

\subsubsection{Statement Deletion:}
\label{subsec:stmtdel}
The basic statement deletion was modeled on the work by Deng et
al.~\cite{deng2013empirical}. The operations on single statements was modeled
using \pitvmc, \pitnvmc, \pitcc, \pitemv, \pitri
for simple statements, and using \pitrc for control structures,
which replaced the boolean condition with false, resulting in removal of
the block of statements. The operator for return values was modeled using
\pitrv, which is similar.  The operators for \textit{while,for},
and \textit{if} statements were modeled using \pitdc,
which replaced the boolean condition with true, which removed the effect
of conditional. The \textit{switch} statement deletion was modeled using
\pitrs which replaced the first 100 labels with default label,
resulting in the switch element getting deleted. (Due to the constraints
of the architecture of PIT only the first 100 labels were replaced). The
\textit{try catch} was not necessary at bytecode level.  Finally, to get an
accurate estimation of the effect of true statement deletion, we grouped
the mutants by line, and considered a single virtual mutant (That is, the
total number of mutants is equal to the total number of lines). Further,
killing any mutant from a line resulted in marking the virtual mutant
for that line as killed. This gave us the mutation score for the virtual
statement deletion operator.  We note that the approximation of simple
statement deletion, especially when arithmetic operators are involved is not
complete. However, as seen in Figure~\ref{fig:op}, the number of mutants
produced by \pitm operator is very small. We also note that our
approximation does not account for the increase in ease of detection when
multiple mutations are combined together due to coupling effect. This also
means that not all the lines may be mutated since there may be no applicable
operators. However, given the constraints of a bytecode based mutation system,
we believe that our procedure is reasonable.
